My wonderful paper

### 2024-12-05 _manuscript/_tex/index.tex
formality

@@

\begin{itemize}
\item
  how to systematically simulate data is still unknown, sensitivity of
  the simulation to the results
\item
  plotting is a critical way to check data and they can still be frame
  into a unit test. it is a open problem to how to encode the
  visualization into the unit tests. Maybe a procedure like confirm plot
  (this looks alright to you) and then press the button to continue
\item
  currently no automated way to generate unit tests. It is interesting
  to see the automation of generating unit tests, although it requires
  the inputs from experts across a wide array of common scenarios.
\item
  There are cost and benefit on setting expectation on different
  granularity. At the lowest level, one may have a plan for each data
  entry and every data handling steps. This requires more work from the
  analysts and may not be practical in practice. For more complex
  analyses, analysts may divide the analysis into sections and set
  expectations for each. They can then focus on the specific sections
  flagged by the tests and sub-divide the sections to set expectation
  and diagnose the analysis in a hierarchical manner.
\item
  (only mention it) Software testing relies on ``oracles'' to provide
  the expected output necessary for verifying test results. For example,
  to test whether the program correctly calculates 1 + 1, one need to
  supply the correct answer, 2. However, establishing this ``correct''
  output can sometimes be challenging, where obtaining a solution may be
  difficult without the program itself. This situation leads to the
  oracle problem \citep{barr2014oracle}. In data analysis, the similar
  oracle problem can happen, as the ``truth'' of an outcome, the
  expectation, depends on the underlying theory or interpretation. For
  example, in a linear regression model, the significance of a
  coefficient may be expected or unexpected based on the theory, making
  it challenging for researcher with a different theory to assess the
  results and the analysis.
\end{itemize}

@@

>>>>

README:

\begin{itemize}
\tightlist
\item
  \emph{Check for TODOs}
\item
  Literature review: Section \emph{diagnosing unexpected outcomes in
  data analysis}
\item
  \emph{Discussion} and \emph{Conclusion}
\item
  In Section \emph{Application}: provide more context on the
  PM10-mortality study and add reference of the {[}0, 0.005{]} PM10
  coefficient
\item
  Roger's Orcid???
\end{itemize}

@@

TODO

\begin{itemize}
\item
  how to systematically simulate data is still unknown
\item
  plotting is a critical way to check data and they can still be frame
  into checks. i.e.~the density/ histogram suggests there are outliers.
  It is a open problem to how to encode the visualization into checks.
\item
  currently no automated way to generate checks. It is interesting to
  see how check generation can be automated, although it requires the
  inputs from experts across a wide array of common scenarios.
\item
  checks are also closely related to the concept of unit tests in
  software engineering. While unit tests are designed to isolate and
  test specific aspects of the code, it is difficult for analysis
  validation check to do so.
\item
  There are cost and benefit on setting expectation on different
  granularity. At the lowest level, one may have a plan for each data
  entry and every data handling steps. This requires more work from the
  analysts and may not be practical in practice. For more complex
  analyses, analysts may divide the analysis into sections and set
  expectations for each. They can then focus on the specific sections
  flagged by the tests and sub-divide the sections to set expectation
  and diagnose the analysis in a hierarchical manner.
\end{itemize}

@@

TODO

\section{Acknowledgement}\label{acknowledgement}

The article is created using Quarto \citep{Allaire_Quarto_2022} in R
\citep{R}. The source code for reproducing the work reported in this
paper can be found at:
\url{https://github.com/huizezhang-sherry/paper-avc}.

### 2024-12-05 index.qmd
formality

@@

-   how to systematically simulate data is still unknown, sensitivity of the simulation to the results

-   plotting is a critical way to check data and they can still be frame into a unit test. it is a open problem to how to encode the visualization into the unit tests. Maybe a procedure like confirm plot (this looks alright to you) and then press the button to continue

-   currently no automated way to generate unit tests. It is interesting to see the automation of generating unit tests, although it requires the inputs from experts across a wide array of common scenarios.

@@

-   (only mention it) Software testing relies on "oracles" to provide the expected output necessary for verifying test results. For example, to test whether the program correctly calculates 1 + 1, one need to supply the correct answer, 2. However, establishing this "correct" output can sometimes be challenging, where obtaining a solution may be difficult without the program itself. This situation leads to the oracle problem [@barr2014oracle]. In data analysis, the similar oracle problem can happen, as the "truth" of an outcome, the expectation, depends on the underlying theory or interpretation. For example, in a linear regression model, the significance of a coefficient may be expected or unexpected based on the theory, making it challenging for researcher with a different theory to assess the results and the analysis.

@@

>>>>

README:

* *Check for TODOs*
- Literature review: Section *diagnosing unexpected outcomes in data analysis* 
- *Discussion* and *Conclusion*
- In Section *Application*: provide more context on the PM10-mortality study and add reference of the [0, 0.005] PM10 coefficient
- Roger's Orcid???

@@

TODO

-   how to systematically simulate data is still unknown

-   plotting is a critical way to check data and they can still be frame into checks. i.e. the density/ histogram suggests there are outliers. It is a open problem to how to encode the visualization into checks.

-   currently no automated way to generate checks. It is interesting to see how check generation can be automated, although it requires the inputs from experts across a wide array of common scenarios.

- checks are also closely related to the concept of unit tests in software engineering. While unit tests are designed to isolate and test specific aspects of the code, it is difficult for analysis validation check to do so.

@@

@@

TODO

# Acknowledgement

The article is created using Quarto [@Allaire_Quarto_2022] in R [@R].
The source code for reproducing the work reported in this paper can be
found at: <https://github.com/huizezhang-sherry/paper-avc>.
